### 2011-11-27 AffineLieAlgebras/Thesis/1.tex
Chapter 2 is completely translated. Description of computational package is moved to the last chapter.

\begin{mynote} The orthogonal subalgebra $\afb$ is always trivial
for conformal embeddings $\af\longrightarrow \mathfrak{g}$.
\begin{proof}
Consider the modes expansion of the energy-momentum tensor
\begin{equation*}
\label{eq:47}
  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n.
\end{equation*}
The modes $L_n$ are constructed as combinations of normally-ordered products of $\gf$-algebra generators,
\begin{equation*}
\label{eq:48}
  L_n=\frac{1}{2(k+h^v)}\sum_{\alpha}\sum_m:X^{\alpha}_m X^{\alpha}_{n-m}: \; .
\end{equation*}
In case of a conformal embedding energy-momentum tensors $T_{\mathfrak{g}}(z)$ and $T_{\af}(z)$ are
equal (see (\ref{eq:2})).

In these combinations we are to substitute  $\af$-generators in terms of $\mathfrak{g}$-generators
and obtain the energy-momentum tensor $T_{\mathfrak{g}}$.
But if the set of generators attributed to $\Delta_{\afb}$ is not empty this is not possible,
since $T_{\mathfrak{g}}$ contains generators $X^{\alpha}_n$ for $\alpha\in \Delta_{\afb}$.
\end{proof}
\end{mynote}

\subsubsection{Special embedding $\hat{A}_1\rightarrow\hat{A}_2$.}
\label{sec:spec-embedd-hata_1s}

Consider the case where both $\gf$ and $\af$ are affine Lie algebras:
$\hat{A}_1 \rightarrow \hat{A}_2$ and the injection is the affine extension of the
special injection $A_1 \rightarrow A_2$ with the embedding index $x_e=4$.
As far as $\gf$-modules to be considered are of level one,
the necessary $\af$-modules will be of level $\tilde{k}=kx_e=4$.

There exist three level one fundamental weights of $\hat{A}_2$.
It is easy to see that the set $\Delta_{ \afb }$ is empty and the subalgebra $\afb=0$.
Then ${\cal D}_{\afb}=0$, $\hf_{\perp}$ is one-dimensional abelian subalgebra and
the dimension of $\tilde\afb=\afb\oplus \hf_{\perp}$ is also 1.
It is convenient to choose the classical root for $\hat{A}_1$ to be
$\beta=\frac{1}{2}(\alpha_1+\alpha_2)$.

Using Definition (\ref{fan-definition})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$.
In this case $\gamma_0 =0$ and its sign $s\left( 0 \right)=-1$ thus we are to use the
sign function $s(\gamma)$ (see Figure \ref{fig:AffineA2A1Fan}).

@@

  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ for $\hat{A_1}\rightarrow \hat{A_2}$
  in the basis $\left\{\beta,\delta \right\}$. Notice that $\gamma_0 =0$, so values of $s(\gamma)$
  are prescribed to the weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

Consider the module $L^{\omega_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
presentation of the highest weight and the finite part
coordinates are the Dynkin indices (see section(\ref{sec:notation})).

The set $\widehat{\Psi^{(\omega_0)}}$  is displayed in Figure
\ref{fig:affine_A2_anom_point} up to the sixth grade.

\begin{figure}[h!tb]
  \hspace*{-1.5cm}
  \includegraphics[width=180mm]{figure7}
  \caption{Singular weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
   The classical (grade zero) cross-section of the diagram is shown separately
   in the right part of the figure.
  We use the orthogonal basis with the unit vector equal to $\alpha_1$.
  The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
by box when $\epsilon(w)=-1$. Simple roots of the classical subalgebra $A_2$ are
grey and the grey diagonal plane corresponds to the Cartan subalgebra of
the embedded algebra $\hat{A}_1$.}
  \label{fig:affine_A2_anom_point}
\end{figure}

The next step is  to project the anomalous weights to $P_{\hat A_1}$.
The result is the element $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
presented in Figure \ref{fig:AffineA2_A1_anom_proj} up to the twelfth grade.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{figure8}
  \caption{The singular element $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
  displayed in $P_{\hat A_1}$
  with the basis $\left\{\beta,\delta \right\}$.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

Using the recurrent relation (\ref{recurrent-relation}) with the fan
$\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ and the singular weights in
$\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
we get the anomalous branching coefficients presented
in Figure \ref{fig:AffineA2_A1_branching}.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{figure9}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$. The boundaries
  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
 are indicated by black lines. Two anomalous highest weights located
 in the main Weyl chamber are marked by stars.
 Both have multiplicity 1, so the branching coefficients for them are equal 1.}
  \label{fig:AffineA2_A1_branching}
\end{figure}
Inside the Weyl chamber $\bar{C}_{\hat{A}_1}$
(its boundaries are indicated in Figure \ref{fig:AffineA2_A1_branching})
there are only two nonzero anomalous weights and both have multiplicity 1.
These are the highest weights of $\af$-submodules and the multiplicities are their branching
coefficients. Thus we get the decomposition
\begin{equation*}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
\end{equation*}
Notice that the finite reducibility theorem holds.

The same fan $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ can be used for any other highest weight
module $L^{\mu}_{\hat{A_2}}$. In particular for irreducible modules of level one  we get the trivial
branching:
\begin{equation*}
  \label{eq:44}
   L^{(1,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)},\\
   L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
\end{equation*}

Using these results the modular-invariant partition function is easily found,
\begin{equation*}
  \label{eq:45}
  Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
\end{equation*}

\subsubsection{Coset models}
\label{sec:coset-models}

Coset models \cite{Goddard198588} tightly connected with the gauged WZW-models are actively studied
in string theory, especially in string models on anti-de-Sitter space
\cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
The characters in coset models are proportional to branching functions,
\begin{equation}
  \label{eq:31}
  \chi^{(\mu)}_{\nu}(\tau)=e^{2\pi i \tau (m_{\mu}-m_{\nu})} b^{(\mu)}_{\nu}(\tau),
\end{equation}
with
\begin{equation*}
  \label{eq:46}
  m_{\mu}=\frac{\left|\mu+\rho\right|^2}{2(k+g)}-\frac{\left|\rho\right|^2}{2g}.
\end{equation*}
The problem of branching functions construction in the coset models was considered
in  \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.

Let us return to our example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
$A_1 \rightarrow B_2$.
Since this embedding is regular and $x_e=1$, the subalgebra modules and the initial module are of the same level.
The set  of positive roots with zero projection
on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case:
$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$ and $\afb=A_1$. It is easy to see that here $\hf_{\perp}$
is trivial and ${\cal D}_{\afb}=0$.

Using Definition (\ref{fan-definition}) we obtain the fan
$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=-1$.
Values of the sign function $s(\gamma)$ for
$ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ are presented in Figure \ref{fig:AffineB2A1Fan}.
We restricted the computation to the twelfth grade.
\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{figure10}
  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$
  for $\hat{A_1}\rightarrow \hat{B_2}$ in the basis $\left\{\beta,\delta \right\}$. Values of  $s(\gamma)$ are shown for the
  weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $\omega_1=(1,0;1;0)$,
where the finite part coordinates are in the orthogonal basis $e_1,e_2$.
The set of anomalous weights for this module up to the sixth grade is presented in Figure \ref{fig:affine_B2_anom_point}.

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{figure11}
  \caption{Singular weights for $L^{(1,0;1;0)}_{\hat B_2 }$. The standard basis $\{e_1,e_2\}$ is used for the classical cross-section.
  The weights in the zero grade are the same as in Figure \ref{fig:B2_A1}.
  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by boxes for $\epsilon(w)=-1$.
Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
of the embedded algebra $\hat{A}_1$.}
  \label{fig:affine_B2_anom_point}
\end{figure}

According to the recursive algorithm \ref{sec:algorithm} we project these anomalous weights to
$P_{\hat{A_1}}$ and find the dimensions of the corresponding
$\afb$-modules $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$.
In the grade zero this projection gives exactly the set
$\Psi ^{\left( \mu \right) }_{\left(  A_1, A_1 \right)}$ for the embedding of
the classical Lie algebra $A_1\rightarrow B_2$. To see this compare Figure \ref{fig:B2_A1}
with Figure \ref{fig:AffineB2_A1_anom_proj}
where the singular element $\Psi ^{\left( \mu \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
for the affine embedding $\hat{A_1}$ is presented up to the twelfth grade.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=120mm]{figure12}
  \caption{Singular element $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
  in the basis $\{\beta,\delta\}$. Dimensions of the corresponding $\afb=A_1$-modules
  with the signs $\epsilon(u)$ are indicated.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

\begin{figure}[h!bt]
  \centering
  \includegraphics[width=120mm]{figure13}
  \caption{Anomalous branching coefficients for $\hat{A_1}\rightarrow \hat{B_2}$. The basis $\{\beta,\delta\}$ is used.
 Boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
 are indicated by black lines. Anomalous branching coefficients
 inside the main Weyl chamber are equal to branching coefficients of the embedding $\hat{A_1}\rightarrow \hat{B_2}$.}
  \label{fig:AffineB2_A1_branching}
\end{figure}

Multiplicities of the highest weights inside the  Weyl chamber
$\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
define the following branching coefficients (up to the twelfth grade),
\begin{eqnarray*}
  \label{eq:28}
  L^{\omega_1}_{\hat{B_2}\downarrow \hat{A_1}}
  &=&2 L_{\hat{A_1}}^{\omega_1}\oplus 1 L_{\hat{A_1}}^{\omega_0}\oplus 4 L_{\hat{A_1}}^{\omega_0-\delta}\oplus\\
    &&2 L_{\hat{A_1}}^{\omega_1-\delta}\oplus 8 L_{\hat{A_1}}^{\omega_0-2\delta}\oplus
    8 L_{\hat{A_1}}^{\omega_1-2\delta}\oplus 15 L_{\hat{A_1}}^{\omega_0-3\delta}\oplus\\
    &&12 L_{\hat{A_1}}^{\omega_1-3\delta}\oplus 26 L_{\hat{A_1}}^{\omega_1-4\delta}\oplus
    29 L_{\hat{A_1}}^{\omega_0-4\delta}\oplus 51 L_{\hat{A_1}}^{\omega_0-5\delta}\oplus\\
    &&42 L_{\hat{A_1}}^{\omega_1-5\delta}\oplus 78 L_{\hat{A_1}}^{\omega_1-6\delta}\oplus
    85 L_{\hat{A_1}}^{\omega_0-6\delta}\oplus 120 L_{\hat{A_1}}^{\omega_1-7\delta}\oplus\\
    &&139 L_{\hat{A_1}}^{\omega_0-7\delta}\oplus 202 L_{\hat{A_1}}^{\omega_1-8\delta}\oplus
    222 L_{\hat{A_1}}^{\omega_0-8\delta}\oplus 306 L_{\hat{A_1}}^{\omega_1-9\delta}\oplus\\
    &&346 L_{\hat{A_1}}^{\omega_0-9\delta}\oplus 530 L_{\hat{A_1}}^{\omega_0-10\delta}\oplus
    482 L_{\hat{A_1}}^{\omega_1-10\delta}\oplus 714 L_{\hat{A_1}}^{\omega_1-11\delta}\oplus\\
    &&797 L_{\hat{A_1}}^{\omega_0-11\delta}\oplus 1080 L_{\hat{A_1}}^{\omega_1-12\delta}\oplus
    1180 L_{\hat{A_1}}^{\omega_0-12\delta}\oplus \dots
\end{eqnarray*}
This result can be presented as the set of branching functions:
\begin{eqnarray*}
  \label{eq:29}
  \begin{array}{cc}
    b^{(\omega_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(\omega_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray*}
Here $q=\exp (2\pi i \tau)$ and the lower index enumerates the branching functions according
to their highest weights in $P^+_{\hat{A_1}}$.
These are the fundamental weights $\omega_0=\lambda_0=(0,1,0),\; \omega_1=\alpha/2=(1,1,0)$.

Now we can return to (\ref{eq:31}),
\begin{equation*}
  \label{eq:35}
  \begin{array}{cc}
    \chi^{(\omega_1)}_{1}(q)= & q^{\frac{7}{12}}\left( 2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\right. \\
    & \left. 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots \right),\\
    \chi^{(\omega_1)}_{0}(q) = & q^{\frac{5}{6}}\left(1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\right. \\
    &\left. 222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\right),
  \end{array}
\end{equation*}
and finally obtain expansions for the $B_2/A_1$-coset characters.

>>>>

\begin{mynote} Ортогональная подалгебра  $\afb$ всегда тривиальна в случае конформного вложения $\af\longrightarrow \mathfrak{g}$.
\begin{proof}
Рассмотрим разложение тензора энергии-импульса на моды:
\begin{equation*}
\label{eq:47}
  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n.
\end{equation*}
Моды $L_n$ представляют собой комбинации нормально упорядоченных произведений генераторов алгебры $\gf$,
\begin{equation*}
\label{eq:48}
  L_n=\frac{1}{2(k+h^v)}\sum_{\alpha}\sum_m:X^{\alpha}_m X^{\alpha}_{n-m}: \; .
\end{equation*}
При конформном вложении тензоры энергии-импульса  $T_{\mathfrak{g}}(z)$ и $T_{\af}(z)$ равны (см. (\ref{eq:2})).

В эти комбинации мы должны подставить генераторы подалгебры $\af$ выраженные через генераторы $\mathfrak{g}$ и получить тензор энергии-импульса $T_{\mathfrak{g}}$. Но если набор генераторов, связанных с  $\Delta_{\afb}$ не пуст, это не возможно, так как  $T_{\mathfrak{g}}$ содержит генераторы $X^{\alpha}_n$, где $\alpha\in \Delta_{\afb}$.
\end{proof}
\end{mynote}

\subsubsection{Специальное вложение $\hat{A}_1\rightarrow\hat{A}_2$.}
\label{sec:spec-embedd-hata_1s}
Рассмотрим следующие пример аффинной алгебры Ли $\gf$ и аффинной подалгебры $\af$:
$\hat{A}_1 \rightarrow \hat{A}_2$ и вложение является аффинным расширением специального вложения $A_1 \rightarrow A_2$ с индексом вложения $x_e=4$. Так как мы должны рассматривать $\gf$-модули уровня один, соответствующие  $\af$-модули будут иметь уровень $\tilde{k}=kx_e=4$.

Существует три фундаментальных веса алгебры  $\hat{A}_2$ имеющих уровень один. 
Легко видеть, что множество $\Delta_{ \afb }$ пусто и подалгебра $\afb=0$. Тогда ${\cal D}_{\afb}=0$, $\hf_{\perp}$ -- одномерная абелева подалгебра и размерность $\tilde\afb=\afb\oplus \hf_{\perp}$ также равна 1. Удобно выбрать классический корень для подалгебры $\hat{A}_1$ равным $\beta=\frac{1}{2}(\alpha_1+\alpha_2)$.

Используем Определение (\ref{fan-definition}) и построим веер $\Gamma_{\hat A_1\to\hat A_2}$. В этом случае $\gamma_0 =0$ и знак  $s\left( 0 \right)=-1$, то есть мы используем знаковую функцию $s(\gamma)$ (см. Рисунок \ref{fig:AffineA2A1Fan}).

@@

  \caption{Веер  $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ для вложения $\hat{A_1}\rightarrow \hat{A_2}$ в базисе $\left\{\beta,\delta \right\}$. Заметим, что  $\gamma_0 =0$ и значения $s(\gamma)$ приписаны к весам $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

Рассмотрим модуль $L^{\omega_0=(0,0;1;0)}$. Здесь мы используем обозначение (конечномерная часть; уровень; грейд)
для старшего веса и координаты конечномерной части даются индексами Дынкина (см. раздел \ref{sec:weights-roots}).

Множество весов $\widehat{\Psi^{(\omega_0)}}$ показано на Рисунке \ref{fig:affine_A2_anom_point} вплоть до шестого грейда.

\begin{figure}[h!tb]
  \hspace*{-1.5cm}
  \includegraphics[width=180mm]{figure7}
  \caption{Сингулярные веса модуля $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$. Классическое сечение (нулевой грейд) диаграммы показано отдельно в правой части рисунка. 
    Мы используем ортогональный базис с единичным вектором, равным $\alpha_1$. Веса $w (\omega_0+\rho)-\rho$ показаны крестами, если $\epsilon(w)=1$ и квадратами при $\epsilon(w)=-1$. Простые корни классической подалгебры  $A_2$ показаны серым, а диагональная плоскость соответствует подалгебре Картана вложенной алгебры $\hat{A}_1$.}
  \label{fig:affine_A2_anom_point}
\end{figure}

Следующий шаг состоит в проектировании сингулярных весов на $P_{\hat A_1}$. В результате получается элемент $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$, изображенный на Рисунке \ref{fig:AffineA2_A1_anom_proj} вплоть до двенадцатого грейда.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{figure8}
  \caption{Сингулярный элемент $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$ показан в $P_{\hat A_1}$ с базисом $\left\{\beta,\delta \right\}$.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

Используя рекуррентное соотношение  (\ref{recurrent-relation}) с веером
$\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ и сингулярными весами $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$, мы получаем сингулярные коэффициенты ветвления, показанные на Рисунке \ref{fig:AffineA2_A1_branching}.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{figure9}
  \caption{Сингулярные коэффициенты ветвления для вложения $\hat{A_1}\subset \hat{A_2}$. Границы главной камеры Вейля $\bar{C}_{\hat{A}_1}$ показаны черными линиями. Два сингулярных веса, расположенные в главной камере Вейля, отмечены звездочками. Они оба имеют кратность 1, то есть соответствующие коэффициенты ветвления равны 1.}
  \label{fig:AffineA2_A1_branching}
\end{figure}
Внутри камеры Вейля $\bar{C}_{\hat{A}_1}$ (ее границы показаны на Рисунке \ref{fig:AffineA2_A1_branching}) находятся только два ненулевых сингулярных веса и оба они имеют кратность 1. Это старшие веса подмодулей $\af$ и их кратности равны коэффициентам ветвления. То есть мы получаем разложение
\begin{equation*}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
\end{equation*}
Заметим, что теорема о конечной приводимости выполняется.

Тот же веер $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ можно использовать для других модулей старшего веса $L^{\mu}_{\hat{A_2}}$. В частности для неприводимых модулей уровня один мы получаем тривиальное ветвление:
\begin{equation*}
  \label{eq:44}
   L^{(1,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)},\\
   L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
\end{equation*}

Используя эти результаты легко получить модулярно-инвариантную статсумму:
\begin{equation*}
  \label{eq:45}
  Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
\end{equation*}

\subsubsection{Coset-модели}
\label{sec:coset-models}

Coset-модели \cite{Goddard198588} тесно связанные с калибровочными ВЗНВ-моделям активно изучаются в теории струн, особенно в струнных моделях в пространстве анти де Ситтера
\cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}. Характера в coset-моделях пропорциональны функциям ветвления.
\begin{equation}
  \label{eq:31}
  \chi^{(\mu)}_{\nu}(\tau)=e^{2\pi i \tau (m_{\mu}-m_{\nu})} b^{(\mu)}_{\nu}(\tau),
\end{equation}
где
\begin{equation*}
  \label{eq:46}
  m_{\mu}=\frac{\left|\mu+\rho\right|^2}{2(k+g)}-\frac{\left|\rho\right|^2}{2g}.
\end{equation*}
Проблема построения функций ветвления для  coset-моделей рассматривалась в работах  \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.

Вернемся к нашему примеру \ref{sec:regul-embedd-a_1} и рассмотрим аффинное расширение вложения $A_1 \rightarrow B_2$. Так как вложение регулярно и индекс $x_e=1$, модули подалгебры и исходный модуль имеют одинаковый уровень. Множество положительных корней с нулевой проекцией на корневое пространство подалгебры  $\hat{A_1}$ то же, что и в конечномерном случае: $\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$ и $\afb=A_1$. Легко видеть, что здесь $\hf_{\perp}$ тривиальна и  ${\cal D}_{\afb}=0$.

Используя Определение (\ref{fan-definition}) мы получаем веер вложения $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$. Заметим, что наименьший вес веера $\gamma_0$ равен нулю и  $s\left( \gamma_0 \right)=-1$. Значения знаковой функции  $s(\gamma)$ для $ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ показаны на Рисунке \ref{fig:AffineB2A1Fan}.
Мы ограничили вычисление двенадцатым грейдом. 
\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{figure10}
  \caption{Веер $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$ для вложения $\hat{A_1}\rightarrow \hat{B_2}$ в базисе $\left\{\beta,\delta \right\}$. Значения $s(\gamma)$ показаны для весов $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

Рассмотрим модуль уровня один $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  со старшим весом  $\omega_1=(1,0;1;0)$, где координаты конечномерной части даны в ортогональном базисе $e_1,e_2$. Множество сингулярных весов для этого модуля вплоть до шестого грейда приведено на Рисунке \ref{fig:affine_B2_anom_point}.

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{figure11}
  \caption{Сингулярные веса модуля $L^{(1,0;1;0)}_{\hat B_2 }$. В классическом сечении используется стандартный базис  $\{e_1,e_2\}$. Веса в нулевом грейде те же, что и на Рисунке \ref{fig:B2_A1}. Веса  $w (\omega_1+\rho)-\rho$ отмечены крестами, если $\epsilon(w)=1$ и квадратами при $\epsilon(w)=-1$. Простые корни классической подалгебры  $B_2$ показаны серым, а диагональная плоскость соответствует подалгебре Картана вложенной алгебры $\hat{A}_1$.}
  \label{fig:affine_B2_anom_point}
\end{figure}

В соответствии с рекурсивным алгоритмом  \ref{sec:algorithm} мы проектируем сингулярные веса на $P_{\hat{A_1}}$ и вычисляем размерности $\afb$-модулей $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$. В нулевом грейде эта проекция дает в точности множество $\Psi ^{\left( \mu \right) }_{\left(  A_1, A_1 \right)}$, соответствующее вложению классической алгебры Ли  $A_1\rightarrow B_2$. Это можно заметить сравнивая Рисунок \ref{fig:B2_A1} и Рисунок \ref{fig:AffineB2_A1_anom_proj}, на котором сингулярный элемент $\Psi ^{\left( \mu \right) }_{\left(  \widehat{A_1}, A_1 \right)}$ для аффинного вложения  $\hat{A_1}\to\hat{B_{2}}$  показан вплоть до двенадцатого грейда.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=120mm]{figure12}
  \caption{Сингулярный элемент $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$ в базисе $\{\beta,\delta\}$. Размерности соответствующих  $\afb=A_1$-модулей со знаками  $\epsilon(u)$ представлены на рисунке.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

\begin{figure}[h!bt]
  \centering
  \includegraphics[width=120mm]{figure13}
  \caption{Сингулярные коэффициенты ветвления для вложения $\hat{A_1}\rightarrow \hat{B_2}$. Использован базис $\{\beta,\delta\}$. Границы главной камеры Вейля $\bar{C}_{\hat{A}_1}$ показаны черными линиями. Сингулярные коэффициенты ветвления внутри главной камеры Вейля равны коэффициентам ветвления для вложения $\hat{A_1}\rightarrow \hat{B_2}$.}
  \label{fig:AffineB2_A1_branching}
\end{figure}

Кратности старших весов внутри главной камеры Вейля
$\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$ определяют следующие значения коэффициентов ветвления (до двенадцатого грейда):
\begin{eqnarray*}
  \label{eq:28}
  L^{\omega_1}_{\hat{B_2}\downarrow \hat{A_1}}
  &=&2 L_{\hat{A_1}}^{\omega_1}\oplus 1 L_{\hat{A_1}}^{\omega_0}\oplus 4 L_{\hat{A_1}}^{\omega_0-\delta}\oplus\\
    &&2 L_{\hat{A_1}}^{\omega_1-\delta}\oplus 8 L_{\hat{A_1}}^{\omega_0-2\delta}\oplus
    8 L_{\hat{A_1}}^{\omega_1-2\delta}\oplus 15 L_{\hat{A_1}}^{\omega_0-3\delta}\oplus\\
    &&12 L_{\hat{A_1}}^{\omega_1-3\delta}\oplus 26 L_{\hat{A_1}}^{\omega_1-4\delta}\oplus
    29 L_{\hat{A_1}}^{\omega_0-4\delta}\oplus 51 L_{\hat{A_1}}^{\omega_0-5\delta}\oplus\\
    &&42 L_{\hat{A_1}}^{\omega_1-5\delta}\oplus 78 L_{\hat{A_1}}^{\omega_1-6\delta}\oplus
    85 L_{\hat{A_1}}^{\omega_0-6\delta}\oplus 120 L_{\hat{A_1}}^{\omega_1-7\delta}\oplus\\
    &&139 L_{\hat{A_1}}^{\omega_0-7\delta}\oplus 202 L_{\hat{A_1}}^{\omega_1-8\delta}\oplus
    222 L_{\hat{A_1}}^{\omega_0-8\delta}\oplus 306 L_{\hat{A_1}}^{\omega_1-9\delta}\oplus\\
    &&346 L_{\hat{A_1}}^{\omega_0-9\delta}\oplus 530 L_{\hat{A_1}}^{\omega_0-10\delta}\oplus
    482 L_{\hat{A_1}}^{\omega_1-10\delta}\oplus 714 L_{\hat{A_1}}^{\omega_1-11\delta}\oplus\\
    &&797 L_{\hat{A_1}}^{\omega_0-11\delta}\oplus 1080 L_{\hat{A_1}}^{\omega_1-12\delta}\oplus
    1180 L_{\hat{A_1}}^{\omega_0-12\delta}\oplus \dots
\end{eqnarray*}
Этот результат можно представить в виде набора функций ветвления:
\begin{eqnarray*}
  \label{eq:29}
  \begin{array}{cc}
    b^{(\omega_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(\omega_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray*}
Здесь $q=\exp (2\pi i \tau)$ и нижний индекс нумерует функции ветвления по их старшим весам в  $P^+_{\hat{A_1}}$, равным фундаментальным весам $\omega_0=\lambda_0=(0,1,0),\; \omega_1=\alpha/2=(1,1,0)$.

Теперь мы можем вернуться к равенству (\ref{eq:31}) и получить выражение для характеров coset-модели $B_2/A_1$:
\begin{equation*}
  \label{eq:35}
  \begin{array}{cc}
    \chi^{(\omega_1)}_{1}(q)= & q^{\frac{7}{12}}\left( 2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\right. \\
    & \left. 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots \right),\\
    \chi^{(\omega_1)}_{0}(q) = & q^{\frac{5}{6}}\left(1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\right. \\
    &\left. 222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\right),
  \end{array}
\end{equation*}
